Informative Autonomous Sampling of Oceanographic Variables Using Joint Excursion Sets

### 2020-05-11 ans_to_reviewers/answers-to-reviewers.tex

%----------------------------------------------------------------------
\title{Informative Autonomous Sampling of Oceanographic Variables Using Joint Excursion Sets
  \\\vspace{5mm}
 Authors response
  \\\vspace{5mm}
\small{Manuscript: AOAS1910-027}}
\author{ }

\date{\today}

\maketitle

We are grateful to the reviewers for their comments and
suggestions. They have all been considered in this revised
version of this manuscript. The principal revisions made to the manuscript are as follows and are done to address the main comments by Editors and Reviewers:

\begin{enumerate}
\item The motivation for excursion sets (ESs) and in particular that of {\bf{multivariate ESs}} has been strengthened. Motivating examples are abundant in medicine where doctors do not solely rely on a single symptom but must see several combined effects before making a diagnosis. Another example is that of photosynthesis where plants and algae produce oxygen only when given enough of every component; light, carbon dioxide and water. Our motivation in this paper is that temperature and salinity, combined, drive several processes in the oceans. For instance, salmon lice larvae are known to depend on relatively high temperature and high salinities to survive. Salmon lice are parasites to salmon, and the bivariate ES for temperature and salinity is hence important to understand for sustainable activities in salmon fisheries.

{\it{Action:}} In the revised manuscript these aspects are largely rewritten in the Introduction, Background, ES definitions and Case Study. This change addresses the comments of AE1, R1 (3,) MORE.

\item The {\bf{statistical methodological contribution}} have been clarified and improved, including definitions of ESs and having more general results related to the integrated Bernoulli variance (IBV) for multivariate processes, using marginal (one-location) entries and for volume calculations requiring multiple locations. The revised version highlights these novel statistical results as a main contribution of the paper.

{\it{Action:}} In the revised manuscript these aspects are largely rewritten in the main body containing novel results for IBV for sums of marginal variances as well as for volumes, while the new Appendix derives the closed form results. This change addresses the comments of E2, AE1, R2 (7), R3 (1), MORE.

\item We realized that a contribution of the current work is available code for statisticians who could try this themselves or even extend it for their own statistical cases. The computer code could of course also be useful to practitioners having related sampling design problems. The {\bf{simulation results and code}} are thoroughly re-worked. Open-source python code is now provided for all the examples used in the paper and also for simulation studies using more nuances statistical models (non-stationary, non-isotropic and non-separable).

{\it{Action:}} The simulation study section is largely modified and it contains pointers to the associated open-source code. This change addresses the comments of R1 (2,3),  MORE.

\item In the initial submission we tried to motivate these kinds of applications carefully, but based on the comments, we see that the {\bf{introduction and background}} were too long. We were not selling the paper enough to professional statisticians, and maybe too much to other scientists who are interested in particular areas of these statistical application. In the revised version we motivate more for statisticians, in particular we emphasize the statistical design problem which is sought solved by AUV with its constraints on navigation and computing resources.

{\it{Action:}} The Introduction and Background sections have been largely rewritten. We now get quicker to the point and engage readers in its both applied statistical focus and the methodological contributions. This change addresses the comments of E1, E4, AE1, R2 (7), R3 (1), MORE.

\item We have further included Cedrid Traveletti as co-author. He has contributed on deriving statistical properties of the methods and on improving the code for open-source quality.

\end{enumerate}
\par \vspace{1em}

@@

Note that the reference to page $X$ is made relative to
the original submitted manuscript given to the reviewers.

%======================================================================
\section*{Editor}
%======================================================================
All changes requested from the editor are listed below and answered on a point-by-point basis.

	\item{Comment:}\label{ec1}

Thank you for submitting your manuscript to The Annals of 
Applied Statistics.  Three referees, an Associate Editor (AE),
and I have read it carefully; reports from all four reviewers,
including particularly constructive reports from Referee 1
(R1R1.pdf; marked manuscript in R1R2.pdf) and the AE (R1AE1.pdf), 
can be downloaded via the links below. We all agree that your 
manuscript offers a potentially useful approach to estimating 
plume boundaries and a sequential design for the data collection
by autonomous underwater vehicles (AUVs). Citing from Referee 3
(R1E1.txt), "the authors have motivated the application well."
In this sense, the paper is consistent with the mission of AOAS.

However, the reports also identify serious shortcomings that 
prevent me from accepting your manuscript for publication at
this time. The reports are rather consistent in the nature of 
the problems that would need to be addressed for an AOAS publication.  
Briefly, these issues include:

\item{1. Intended audience:}\label{r3c1}

As you know from reading the Manuscript Submission page of our
web site (from where you submitted your manuscript), "AOAS is 
intended to be read by all professional statisticians, as well 
as by other scientists who are interested in particular areas 
of statistical application. It is important for the abstract
and introduction to say: Why the topic is of interest, and What 
is to be shown, in as non-technical a manner as possible."
Remarks from the AE (point 1), Referee 1 (point 4), and Referee 2 
(R1R3.pdf, 1) refer to this question: "Who is the intended
audience?"  Quoting from Referee 1, "I am not clear about the 
intended audience for this paper.  Or to put it another way, 
for whom is this paper important?" The reports have some 
suggestions that may guide you in making the necessary critical 
revisions along these lines.

\reply: The comment by you, AE and reviewers made us realize that the initial submission had a motivation which was too applied. We were not selling the paper contributions in early enough, and it was not targeted sufficiently to professional statisticians. In the revised version we motivate more for statisticians. (See also comment 4 in the list of main changes above.)

\action: Our actions are to i) rewrite Introduction and Background sections to catch our intended audience and highlight our contributions, ii) restructure the presentation to highlight both statistical contributions as well as the impact such technologies and applied questions could provide for statisticians.

\item{2. Novelty:}\label{r3c2}

As noted in the AOAS mission statement, papers are expected
to include some degree of "methodological innovation."
In separate comments to the Editors, one reviewer noted,
"Methodological novelty is an issue with this paper.  Much of 
it is either standard Gaussian process calculations/formulae 
or sequential designs that were, in all but one case, previously 
proposed. Two things that could add a lot would be good code 
that others could run for the simulation studies like the authors' 
(if someone else were contemplating a similar experiment), and 
good code for finding the optimum design. That could lead to a 
fairly substantial impact of their work."

\reply: We realize that we did not stress the statistical novelty sufficiently in the submitted version. The main statistical novelty is in the closed form calculation for the design criteria of the integrated Bernoulli variance (IBV) associated with excursion sets (ESs) for multivariate processes. In the revised version this is extended to volumes (going beyond single location). We believe that part of the problem with the initial submission was the organization of these new results in the structure of the paper. This is hence re-structured in the revision.

\action: Our actions are to i) extend the closed form calculations to a criterion working on ES volume calculations (going beyond single location), ii) restructure the presentation to work directly on $p$-variate random fields and hence generalize the presentation, iii) restructure the closed form results to be presented in the main body, but with proofs in the new Appendix.

\item{3. Assumptions }\label{r3c3}

Referees 1 and 2, as well as the AE, call attention to some of
the assumptions (e.g., stationary and isotropic random fields),
and ask you to address how realistic they are.

\reply: At this spatial scale there is often not so much data to infer a detailed statistical model, and this is the reason for our parsimonious construction for the real-data case. In other related situations, for instance that of larger fjord, ocean fronts, which are at a larger scale, there would usually be more data available for instance in the form of satellite data or from ensembles of computer model simulations. For such cases, we agree that it would make sense to embed more nuanced models, for instance that of larger variances at certain locations and stronger correlations in certain directions, but for our field trial here we attempted to have as few parameters as possible and had no reason to assume more complicated forms.

That said, in the updated simulation study, which we have generalized and made open-source there are opportunities and examples of more complex covariance models (non-stationary and non-separable and non-isotropic), but we do not conduct any inference for parameters in these models from ocean model data.

\action: Our actions include i) a better description of our parameter choices for the synthetic case and the specification for the real-data case, and ii) brief notes of the extended opportunities available for the associated open-access code, iii) references to related papers (including one of our own) that explored non-stationary Gaussian models for oceanographic phenomena at a larger scale than what is used here.

\item{Major comment 4. Exposition}\label{r3c4}

Both the AE and Referee 1 strongly advise shortening the first
five pages - or, at least, getting to the point (currently on p6)
much sooner.  Quoting from  Referee 1, 5: "I slogged through the 
first six [pages] before I discovered what the paper was to be 
about, on page 6."  You do not want to lose your readers, so I
advise you to engage them early on.  All four reviewers note
potential technical or typographical errors, so please proofread
carefully.

\reply: Based on the comments by yourself, AE and referees, we realize that the motivation part of the paper was too long.

\action: Our actions include a much shorter Section 2 with background. We now aim to engage readers earlier on with the applied statistical focus and methodological contribution of our work.

%======================================================================
 \section*{Associate Editor}
%======================================================================
All changes requested from the editor are listed below and answered on a point-by-point basis.

@@

%======================================================================
\section*{Answers to referee 3}
%======================================================================
All changes requested from Reviewer 3 are listed below and answered on a point-by-point basis.

\setcounter{reviewer}{4}

\begin{answers}

\item{Comment:}\label{r3c1}

\reply: I think this is an interesting paper. The paper is well written, 
and the authors have motivated the application well. 
The authors indicate several paths forward for work in this area, which I think pose interesting questions. They may want to elaborate a bit more on those.

### 2020-05-11 main_new.tex
First draft of answer-letter. to be continued.

Monitoring the world's oceans has gained increased importance in 
light of the changing climate and increasing anthropogenic impact. A
central problem for understanding these factors is the lack of
representative data with sufficient resolution. Most of this
\emph{undersampling} can be attributed to the large spatio-temporal
variations on which ocean processes transpire, prompting the need for
effective means of sampling. By \emph{sampling}, we refer to the design
of observational strategies in the spatial domain, where the use of
autonomous platforms can be combined with statistical methods to pursue
measurements with high scientific relevance.

Traditional data collection at sea has typically been based on static
buoys, Lagrangian floats, or ship-based methods, with significant
logistical limitations that directly impact coverage and sampling
resolution. Modern methods using satellite remote-sensing provide
large-scale coverage but have limited resolution, are limited to
sensing the surface of the ocean, and are impacted by cloud cover. The
advent of robust mobile robotic platforms \citep{Bellingham07} has
resulted in significant contributions to environmental monitoring and
sampling. In particular, autonomous underwater vehicles (AUVs), have
advanced the state of sampling and consequently have made robotics an
integral part of ocean observation; our previous work has contributed
to this effort \citep{das11b,Das2015,fossum18b,fossuminformation}. Other statistical
work in the oceanographic domain include \cite{wikle2013modern}
focusing on hierarchical statistical models; \cite{sahu2008space},
studying spatio-temporal models for sea surface temperature and
salinity data; and \cite{mellucci2018oceanic} looking at the
statistical prediction of features using an underwater glider.

The potential that lies in using information-based methods, which we
highlight in this paper, is to do efficient environmental sampling and
overcome three common challenges, namely:

@@

Addressing this, the combination of statistical tools and robotic platforms is a
natural symbiosis which enables information-based sensing. Central to
this is the ability to model spatially-correlated variables and
provide formal measures of uncertainty. In our formulation we use
Gaussian Processes (GPs) in large part because they allow for
efficient implementation and evaluation in real time onboard a robotic platform.

@@

% The processes occurring in the upper water-column and the photic zone
% (upper sunlit zone) are of vital importance for long-term sustainable
% management of the greater marine ecosystem, climate, and human health.
% With the onset of the warming oceans and increased anthropogenic
% pressure, it is critical to improve our understanding of the associated
% ecosystem response.

% owing to current observation practices.

Central to understanding the changes taking place in the upper
water-column is an understanding of biophysical interaction driven by
an agglomeration of physical forcing (wind, topography, bathymetry,
tidal influences, and local geography, such as fresh water inflows) and
incipient micro-biology driven by planktonic and coastal anthropogenic
input, such as pollution and agricultural runoff transported into the ocean by rivers and streams. These often result
in a range of ecosystem-related phenomena such as blooms, anoxic zones
and plumes, all of which have significant direct and indirect effects
on society. Walter Munk referred to the 20\textsuperscript{th} century
as the \emph{century of undersampling} \citep{munk2002}, pointing out
a lack of sufficient sampling resolution in time and space as a
critical issue for characterizing ocean phenomena. Even today,
policymakers struggle with limited observability of severe
environmental problems; a prominent example is the recent (May 2018)
outbreak of harmful algal blooms in Northern Norway\footnote{Report
  from the Institute of Marine Research: https://bit.ly/2KZGJfI}, with
losses exceeding 12 million tons of salmon valued at \$80 million
(Norwegian Directorate of Fisheries). This is a case in point of how
adequate sampling efforts could have provided a more accurate
assessment and early warning of changing environmental
conditions. These challenges related to undersampling have been
driving ocean sensing practices towards more autonomous, networked,
and distributed use of robotic assets in order to fill the gaps in our
understanding (See Fig. \ref{fig:envir1}), where observation is guided
by assimilation of recent measurements and statistical models.

\begin{figure}[!h] 
  \centering 
  \subfigure[Illustration of an ocean sensing network and the sense-plan-act control methodology.]{\includegraphics[width =
    0.49\textwidth]{Figures/envir2.pdf}\label{fig:envir1}}
  \hfill
  \subfigure[Frontal patterns off of the Nidelva river, Trondheim, Norway.]{\includegraphics[width =
    0.49\textwidth]{Figures/river_proccess.pdf}\label{fig:nidelven}}
  \caption{\ref{fig:envir1} Traditional ocean observation based on
    ship-based sampling has recently been augmented by autonomous and
    collaborative networked operations of robotic vehicles to resolve
    numerous bio-geochemical processes and their interactions. The
    sense-plan-act control approach to autonomous control can reason
    and make decisions for efficient onboard adaptive sampling.
    \ref{fig:nidelven} The interaction of river and ocean creates
    processes that are challenging to map, where the combination of
    statistics and robotics can play a vital role in enabling more
    effective observation practices.}
\label{fig:envir}
\end{figure}

Our focus in this work is towards spatial characterization of a
frontal system specifically, fronts generated by river
plumes. Fig. \ref{fig:nidelven} shows the survey area (the outlet of
the Nidelva river, Trondheim, Norway) where cold freshwater enters
from the river, creating a strong gradient in both temperature and
salinity. Because of the local topography and the Coreolis force
\citep{coriolis1835memoire} the cold fresh water tends to flow near
land to the east. Depending on the river discharge, tidal effects,
wind, and temperature differences, this boundary often gets
distorted. Initial knowledge about the location and evolution of these
features is therefore highly uncertain, making deterministic planning
challenging.

@@

River plumes belong to a class of ocean processes that are local and
act on smaller \emph{sub-mesoscale} extent (from $5 m^2$ -- $10 km^2$) where
lateral spatial variability tends to dominate. Remote sensing and
synthetic ocean models often find it challenging to provide detail at
this scale \citep{Lermusiaux:2006} and the principal way to resolve
for fine resolution is by direct in-situ observation. At larger
\emph{mesoscale} ($>50 km^2$), both three-dimensional space and time
dynamics are important and can shift substantially, while in the case
of river plumes one can often limit the scope to cover only lateral
spatial elements. However, the methodological framework can be
extended to higher dimensional situations in a similar manner.

@@

AUVs are used to gather in-situ spatio-temporal data while carrying a
range of scientific payloads to survey the water column. Typically,
they operate at $\sim 1-3$ m/s, can reach depths from 100--6000 m with
an in-water operation time capacity dependent on survey speed, payload
sensors and mission design. By deploying AUVs together with other
resources, one can augment information from synthetic ocean models,
remote-sensing data, or fixed-location sensors on buoys. Traditional
operations and surveys with AUVs are usually limited to observations
along fixed transects on a spatial grid, pre-programmed by the human
operator. A more effective approach is to instead use onboard algorithms to continuously evaluate,
update, and refine future sampling locations (sense-plan-act cycle in Fig. \ref{fig:envir1}), making the information
gathering \emph{adaptive} and \emph{contextual} to the survey
requirements \citep{das11b,fossum18b,fossuminformation}. The space of
sampling opportunities can still be limited to a grid, but adaptation
allows more flexibility. For instance, an AUV could reconstruct or
modify a survey line based on what temperatures it is measuring by
using embedded methods in decision-theoretic planning
\citep{py10,Rajan12,Rajan12b}.

@@

\begin{figure}[h!]
\centering
\includegraphics[width=0.50\textwidth]{Figures/sim/wp_graph_paper.pdf}
\caption{The equilateral waypoint graph used to discretize the
  trajectory choices over the $31\times31$ grid used to discretize the GP.}
\label{fig:wp_graph}
\end{figure}

>>>>

Monitoring the world's oceans has gained increased importance in 
light of the changing climate and increasing anthropogenic impact. A
central problem for understanding these factors is the lack of
representative data with sufficient resolution. Most of this
\emph{undersampling} can be attributed to the large spatio-temporal
variations on which ocean processes transpire, prompting the need for
effective means of sampling. By \emph{sampling}, we refer to the design of observational strategies in the spatial domain, where the use of autonomous platforms can be combined with statistical methods to pursue measurements with high scientific relevance. The potential that lies in using information-based methods \citep{das11b,Das2015,fossum18b,fossuminformation}, which we highlight in this paper, is to do efficient environmental sampling and overcome three common challenges, namely:

% After reviews: - This is moved to Section 2.1.

%Traditional data collection at sea has typically been based on static
%buoys, Lagrangian floats, or ship-based methods, with significant
%logistical limitations that directly impact coverage and sampling
%resolution. Modern methods using satellite remote-sensing provide
%large-scale coverage but have limited resolution, are limited to
%sensing the surface of the ocean, and are impacted by cloud cover. The
%advent of robust mobile robotic platforms \citep{Bellingham07} has
%resulted in significant contributions to environmental monitoring and
%sampling. In particular, autonomous underwater vehicles (AUVs), have
%advanced the state of sampling and consequently have made robotics an
%integral part of ocean observation; our previous work has contributed
%to this effort \citep{das11b,Das2015,fossum18b,fossuminformation}. Other ¤ %statistical work in the oceanographic domain include \cite{wikle2013modern}
%focusing on hierarchical statistical models; \cite{sahu2008space},
%studying spatio-temporal models for sea surface temperature and
%salinity data; and \cite{mellucci2018oceanic} looking at the
%statistical prediction of features using an underwater glider.

@@

Addressing this, the combination of statistical tools and robotic platforms is a
natural symbiosis which enables information-based sensing. Central to
this is the ability to model spatially-correlated variables and
provide formal measures of uncertainty. Our formulation is based on
Gaussian Processes (GPs) as they allow efficient implementation 
and evaluation in real time onboard a robotic platform.

@@

% The processes occurring in the upper water-column and the photic zone
% (upper sunlit zone) are of vital importance for long-term sustainable
% management of the greater marine ecosystem, climate, and human health.
% With the onset of the warming oceans and increased anthropogenic
% pressure, it is critical to improve our understanding of the associated
% ecosystem response.
% owing to current observation practices.

Central to understanding the changes taking place in the upper
water-column is an understanding of biophysical interaction driven by
an agglomeration of physical forcing (wind, topography, bathymetry,
tidal influences, and local geography, such as fresh water inflows) and
incipient micro-biology driven by planktonic and coastal anthropogenic
input, such as pollution and agricultural runoff transported into the ocean by rivers and streams. These often result in a range of ecosystem-related phenomena such as blooms, anoxic zones and plumes, all of which have significant direct and indirect effects on society.

% On observation and why robotics
Traditional data collection at sea has typically been based on static
buoys, Lagrangian floats, or ship-based methods, with significant
logistical limitations that directly impact coverage and sampling
resolution. Modern methods using satellite remote-sensing provide
large-scale coverage but have limited resolution, are limited to
sensing the surface of the ocean, and are impacted by cloud cover. The
advent of mobile robotic platforms \citep{Bellingham07} has
resulted in significant contributions to environmental monitoring and
sampling. In particular, autonomous underwater vehicles (AUVs), have
advanced the state of sampling and consequently have made robotics an
integral part of ocean observation. The previously listed challenges related to undersampling have also been driving ocean sensing practices towards more autonomous, networked, and distributed use of robotic assets (See Fig. \ref{fig:envir1}), where observation is guided by assimilation of recent measurements and statistical models.

%Walter Munk referred to the 20\textsuperscript{th} century
%as the \emph{century of undersampling} \citep{munk2002}, pointing out
%a lack of sufficient sampling resolution in time and space as a
%critical issue for characterizing ocean phenomena. Even today,
%policymakers struggle with limited observability of severe
%environmental problems; a prominent example is the recent (May 2018)
%outbreak of harmful algal blooms in Northern Norway\footnote{Report
%  from the Institute of Marine Research: https://bit.ly/2KZGJfI}, with
%losses exceeding 12 million tons of salmon valued at \$80 million
%(Norwegian Directorate of Fisheries). This is a case in point of how
%adequate sampling efforts could have provided a more accurate
%assessment and early warning of changing environmental conditions.

\begin{figure}[!h] 
  \centering 
  \subfigure[Illustration of an ocean sensing network and the sense-plan-act control methodology.]{\includegraphics[width =
    0.49\textwidth]{Figures/envir2.pdf}\label{fig:envir1}}
  \hfill
  \subfigure[Frontal patterns off of the Nidelva river, Trondheim, Norway.]{\includegraphics[width =
    0.49\textwidth]{Figures/river_proccess.pdf}\label{fig:nidelven}}
  \caption{\ref{fig:envir1} Traditional ocean observation based on
    ship-based sampling has recently been augmented by autonomous and
    collaborative networked operations of robotic vehicles to resolve
    numerous bio-geochemical processes and their interactions. AUV platforms are an integral part of this network being able to reason and make decisions for efficient onboard adaptive sampling using the sense-plan-act control approach to autonomous control.
    \ref{fig:nidelven} The interaction of river and ocean creates
    processes that are challenging to map, where the combination of
    statistics and robotics can play a vital role in enabling more
    effective observation practices.}
\label{fig:envir}
\end{figure}

The application that is of focus in this work is towards spatial characterization of a frontal system specifically, fronts generated by river
plumes. Fig. \ref{fig:nidelven} shows the survey area (the outlet of
the Nidelva river, Trondheim, Norway) where cold freshwater enters
from the river, creating a strong gradient in both temperature and
salinity. Because of the local topography and the Coreolis force
\citep{coriolis1835memoire} the cold fresh water tends to flow near
land to the east. Depending on the river discharge, tidal effects,
wind, and temperature differences, this boundary often gets
distorted. Initial knowledge about the location and evolution of these
features is therefore highly uncertain, making deterministic planning
challenging. River plumes belong to a class of ocean processes that are local and
act on smaller \emph{sub-mesoscale} extent (from $5 m^2$ -- $10 km^2$) where
lateral spatial variability tends to dominate. Remote sensing and
synthetic ocean models often find it challenging to provide detail at
this scale \citep{Lermusiaux:2006} and the principal way to resolve
for fine resolution is by direct in-situ observation. At larger
\emph{mesoscale} ($>50 km^2$), both three-dimensional space and time
dynamics are important and can shift substantially, while in the case
of river plumes one can often limit the scope to cover only lateral
spatial elements. However, the methodological framework can be
extended to higher dimensional situations in a similar manner.

@@

@@

AUVs are used to gather in-situ spatio-temporal data while carrying a
range of scientific payloads to survey the water column. Typically,
they operate at $\sim 1-3$ m/s, can reach depths from 100--6000 m with
an in-water operation time capacity dependent on survey speed, payload
sensors and mission design. AUVs have limited computational capacity due to their limited energy and payload space. The computations is usually done on a single-board computer (SBC), like the Raspberry Pi or an multicore GPU NVIDIA Jetson TX1.

By deploying AUVs together with other
resources, one can augment information from synthetic ocean models,
remote-sensing data, or fixed-location sensors on buoys. Traditional
operations and surveys with AUVs are usually limited to observations
along fixed transects on a spatial grid, pre-programmed by the human
operator. A more effective approach is to instead use onboard algorithms to continuously evaluate,
update, and refine future sampling locations (sense-plan-act cycle in Fig. \ref{fig:envir1}), making the information
gathering \emph{adaptive} and \emph{contextual} to the survey
requirements \citep{das11b,fossum18b,fossuminformation}. The space of
sampling opportunities can still be limited to a grid, but adaptation
allows more flexibility. For instance, an AUV could reconstruct or
modify a survey line based on what temperatures it is measuring by
using embedded methods in decision-theoretic planning
\citep{py10,Rajan12,Rajan12b}.

@@

%\begin{figure}[h!]
%\centering
%\includegraphics[width=0.50\textwidth]{Figures/sim/wp_graph_paper.pdf}
%\caption{The equilateral waypoint graph used to discretize the
%  trajectory choices over the $31\times31$ grid used to discretize the GP.}
%\label{fig:wp_graph}
%\end{figure}

\begin{figure}[!h] 
\centering 
\subfigure[The waypoint graph.]{\includegraphics[width =
0.49\textwidth]{Figures/sim/wp_graph_paper.pdf}\label{fig:wp_graph_a}}
\hfill
\subfigure[The waypoint graph in 3D.]{\includegraphics[width =
0.49\textwidth]{Figures/sim/wp_graph_3d.pdf}\label{fig:wp_graph_b}}
\caption{\ref{fig:wp_graph_a} The equilateral waypoint graph used to discretize the
trajectory choices over the $31\times31$ grid used to discretize the GP.
\ref{fig:wp_graph_b} The waypoint grid shown in a 3D environment.}
\label{fig:wp_graph}
\end{figure}
